---
title: "1. EDA"
author: "Chisung Song"
date: "2016. 3. 18"
output:
  html_document:
    keep_md: yes
---

# [1] Exploratory data analysis  

- leanpub의 The Art of Data Science(https://leanpub.com/artofdatascience) 중 chapter4 EDA의 방법을 이용하여 EDA.
- data : https://www.kaggle.com/c/airbnb-recruiting-new-user-bookings

## Step 1. formulate your question
- which country a new user's first booking destination will be

```{r}

```



## Step 2. Read in your data 

### 1. read the data
```{r}
#install.packages("readr")
library(readr)

## the training set of users
df_train <- read_csv("data/train_users_2.csv") # col_types = "ccincc..." 으로 불러올 값 설정 가능.

## the test set of users
df_test <- read_csv("data/test_users.csv")

## web sessions log for users
df_sessions <- read_csv("data/sessions.csv")

## summary statistics of destination countries in this dataset and their locations
df_countries <- read_csv("data/countries.csv")

## summary statistics of users' age group, gender, country of destination
df_people <- read_csv("data/age_gender_bkts.csv")
```

### 2. column name tunning
```{r}
names(df_train) <- make.names(names(df_train))
names(df_test) <- make.names(names(df_test))
names(df_sessions) <- make.names(names(df_sessions))
names(df_countries) <- make.names(names(df_countries))
names(df_people) <- make.names(names(df_people))
```


## Step 3. Check the packaging 
- nrow(), ncol(), dim(), str() 등을 이용하여 데이터의 구조 확인.
```{r}
str(df_train)
str(df_test)
str(df_sessions)
str(df_countries)
str(df_people)
```


## Step 4. Look at the top and the bottom of your data   
```{r}
head(df_train)
head(df_test)
head(df_sessions)
head(df_countries) 
head(df_people)
# 데이터의 끝에 코멘트를 달아두는 경우도 있기 떄문에 tail()도 유용.
```



## Step 5. Check your "n"s
```{r}
library(dplyr)

dim(df_train)
df_train_NNDF <- df_train %>% filter(country_destination != "NDF")
dim(df_train_NNDF)

dsti <- table(df_train_NNDF$country_destination)
barplot(dsti)

barplot(table(df_train$gender))

dim(df_train)

df_train_filtered <- df_train %>% filter(gender != "-unknown-" & gender != "OTHER" & !is.na(age) & !is.na(first_affiliate_tracked) & first_browser != "-unknown-")

table(df_train$first_affiliate_tracked)

library(ggplot2)
  
barplot(table(df_train_filtered$age))


  

barplot(table(df_train_temp$age[1:30]))


df_train$age[1:30]



df_train_temp <- df_train %>% filter(gender != "-unknown-" | age != NA)
df_train_temp <- df_train %>% filter(gender != "-unknown-")  %>% filter(i) 




```



## Step 6. Validate with at least one external data source  
```{r}
library(dplyr)
# 1. country destination 수 비교
dim(df_train)
unique(df_train$country_destination) # ->12가지의 경우.
df_train_NNDF <- df_train %>% filter(country_destination != "NDF")
dim(df_train_NNDF)  

dsti <- table(df_train_NNDF$country_destination)
barplot(dsti)

```



## Step 7. Make a plot           



## Step 8. Try the easy solution first    




## Step 9. Follow up            





------

## naive bayes

```{r}
df_train


```


## naive bayes

```{r}


df_temp <- df_train_filtered %>% filter(country_destination != "NDF")
  

# create train/text indices from toy spam data
ndx <- sample(nrow(df_temp), floor(nrow(df_temp) * 0.7))
train <- df_temp[ndx,]
test <- df_temp[-ndx,]

# split into train/test data
xTrain <- train[,-16]
yTrain <- train$country_destination
xTest <- test[,-16]
yTest <- test$country_destination

xTest

# fit naive bayes model with default params
model <- naiveBayes(xTrain, yTrain)


# look at confusion matrix
table(predict(model, xTest), yTest)
predict(model, xTest)

# plot histogram of predicted probabilities
# note overconfident predictions
probs <- predict(model, xTest, type="raw")
qplot(x=probs[, "spam"], geom="histogram")

# plot ROC curve
pred <- prediction(probs[, "spam"], yTest)
perf_nb <- performance(pred, measure='tpr', x.measure='fpr')
plot(perf_nb)


```



