---
title: "1. EDA"
author: "Chisung Song"
date: "2016. 3. 18"
output: html_document
---

# [1] Exploratory data analysis  

- leanpub의 The Art of Data Science(https://leanpub.com/artofdatascience) 중 chapter4 EDA의 방법을 이용하여 EDA.
- data : https://www.kaggle.com/c/airbnb-recruiting-new-user-bookings

## Step 1. formulate your question
- which country a new user's first booking destination will be

```{r}

```



## Step 2. Read in your data 

### 1. read the data
```{r}
#install.packages("readr")
library(readr)

## the training set of users
df_train <- read_csv("data/train_users_2.csv") # col_types = "ccincc..." 으로 불러올 값 설정 가능.

## the test set of users
df_test <- read_csv("data/test_users.csv")

## web sessions log for users
df_sessions <- read_csv("data/sessions.csv")

## summary statistics of destination countries in this dataset and their locations
df_countries <- read_csv("data/countries.csv")

## summary statistics of users' age group, gender, country of destination
df_people <- read_csv("data/age_gender_bkts.csv")
```

### 2. column name tunning
```{r}
names(df_train) <- make.names(names(df_train))
names(df_test) <- make.names(names(df_test))
names(df_sessions) <- make.names(names(df_sessions))
names(df_countries) <- make.names(names(df_countries))
names(df_people) <- make.names(names(df_people))
```


## Step 3. Check the packaging 
- nrow(), ncol(), dim(), str() 등을 이용하여 데이터의 구조 확인.
```{r}
str(df_train)
str(df_test)
str(df_sessions)
str(df_countries)
str(df_people)
```


## Step 4. Look at the top and the bottom of your data   
```{r}
head(df_train)
head(df_test)
head(df_sessions)
# 데이터의 끝에 코멘트를 달아두는 경우도 있기 떄문에 tail()도 유용.
tail(df_countries) 
tail(df_people)
```



## Step 5. Check your "n"s
```{r}
 

```





## Step 6. Validate with at least one external data source  
## Step 7. Make a plot           
## Step 8. Try the easy solution first    
## Step 9. Follow up            










